A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-08 paper/main.tex
More TODO
delete to dos that are essentially comments

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e. the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging putting words into 15 grammatical categories, a detailed
part-of-speech tagging putting words into 43 grammatical categories, syntactic
dependencies within each sentence, and a semantic analysis based on word
embeddings representing each word in a 300-dimensional semantic space.
This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
\end{abstract}

@@

\todo[inline]{revised: data-driven vs./in combination (with) model-driven}
% data-driven methods
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. However, data-driven methods alone fall usually short
of pinpointing their results to specific, time-locked stimulus features \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to
investigate how hemodynamic brain responses in isolated regions correlate with
stimulus features. They can explain not just ``how'' the brain is responding to
a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

\todo[inline]{revised: why this anno is better than any previous anno and worth
being published as a paper}
% we:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onset and offset of each
sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
audio-description (i.e. the audio-only variant of the
movie)\citep{ForrestGumpGermanAD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why even bother?
This publication enables researchers to model hemodynamic brain responses that
correlate with a variety of aspects of spoken language ranging from a speaker's
identity, to phonology, grammar, and semantics.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimulus.

@@

\subsection*{Data Legend} \todo[inline]{Minimale Info hier, dass es zwei
Versionen gibt und sich der folgende Abschnitt auf TSV file bezieht}
% TextGrid vs. TSV
The annotation is available in two different versions, both providing the same
information: a) as a (text-based) Praat TextGrid file and b) as a text-based,
tab-separated value (TSV) formatted table.
% preview of following subsubsections
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence,
word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
\texttt{stop}, \texttt{vector}.

@@

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; COH: sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this mean; CH: hope it got clearer now}.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
modeled as boxcar function from onset to offset of the corresponding
phoneme.\todo{Does that mean they share events with "other"; CH: dunno what you
mean, but text should be clearer now}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
\todo{Why? Above it says 'we tested if similar linguistic concepts providing
    high semantic information (proper nouns and nouns)'. What does this need
sentences for? CH: it is kinda nuisance regressor}
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? CH: words where chosen to carefully; intervals don't
contain any audible speech with >98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the
average length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous information about auditory features (left-right
difference in volume and root mean squared volume) that was averaged across the
length of every movie frame (\unit[40]{ms}) to capture variance correlating with
low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design
% motion parameter are filtered, too. See FSL manual:
% ``All (confound) EVs will be filtered to match the processing applied to the
% input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time
series.

@@

\todo[inline]{Lass uns bzgl. der Discussion am besten unterhalten; im Grunde
geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins
Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl. Areale
durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie
dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}

% Discussion words > no-speech
For the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled}.
% dissimilarities
\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
references} Contrary to previous studies \citep{ferstl2008extended,
mar2011neural}, we do not find increased medial activation in the precuneus or
medial frontal cortex. This could be attributed to the fact that the contrast
here was not designed to capture social aspects of the narrative.\todo{check the
previous studies}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation that is partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
    If you knew all these issues, why did you do it then? hindsight bias/HARKing
after exploratory analyses?!}.
% but...
Nevertheless and more importantly to exploratorily access the validity of the
dataset is the fact that two similar linguistic concepts (nouns and proper
nouns) embedded in a naturalistic stimulus that was not designed for linguistic
research lead to similar activation patterns\todo{That statement is only true,
if both contrasts are not (solely) driven by the conjunctions. There is no
evidence in the paper that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).

>>>>

\todo{Wort zur Validierungsstudie; awesomeness (s. Aliko (2020); Es sind erst
110 von max 300 Worten verbraucht; Werte runden statt newcommand benutzen}
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e. the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging putting words into 15 grammatical categories, a detailed
part-of-speech tagging putting words into 43 grammatical categories, syntactic
dependencies within each sentence, and a semantic analysis based on word
embeddings representing each word in a 300-dimensional semantic space.
This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
\end{abstract}

@@

% data-driven methods
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. However, data-driven methods alone fall usually short
of pinpointing their results to specific, time-locked stimulus features \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to
investigate how hemodynamic brain responses in isolated regions correlate with
stimulus features. They can explain not just ``how'' the brain is responding to
a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

% we:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onset and offset of each
sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
audio-description (i.e. the audio-only variant of the
movie)\citep{ForrestGumpGermanAD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why even bother?
\todo[inline]{importance/bottleneck of (missing) annotations -> Aliko (2020)}
This publication enables researchers to model hemodynamic brain responses that
correlate with a variety of aspects of spoken language ranging from a speaker's
identity, to phonology, grammar, and semantics.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimulus.

@@

\subsection*{Data Legend}
% TextGrid vs. TSV
The annotation is available in two different versions, both providing the same
information: a) as a (text-based) Praat TextGrid file and b) as a text-based,
tab-separated value (TSV) formatted table.
% preview of following subsubsections
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence,
word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
\texttt{stop}, \texttt{vector}.

@@

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
modeled as boxcar function from onset to offset of the corresponding
phoneme.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the
average length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous information about auditory features (left-right
difference in volume and root mean squared volume) that was averaged across the
length of every movie frame (\unit[40]{ms}) to capture variance correlating with
low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design
% motion parameter are filtered, too. See FSL manual:
% ``All (confound) EVs will be filtered to match the processing applied to the
% input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time
series.

@@

% Discussion
% words > no-speech
For the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled, wilson2007beyond}.
% dissimilarities
\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
references} Contrary to previous studies \citep{ferstl2008extended,
mar2011neural}, we do not find increased medial activation in the precuneus or
medial frontal cortex. This could be attributed to the fact that the contrast
here was not designed to capture social aspects of the
narrative.\todo{wilson2007beyond: ISC medial ja, aber decreased activation
    compared to rest; current study in reverse contrast: posterior cingulate and
anterior cingulate (and insula bilaterally)}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation that is partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
    If you knew all these issues, why did you do it then? hindsight bias/HARKing
after exploratory analyses?!}.
% but...
Nevertheless and more importantly to exploratorily access the validity of the
dataset is the fact that two similar linguistic concepts (nouns and proper
nouns) embedded in a naturalistic stimulus that was not designed for linguistic
research lead to similar activation patterns\todo{That statement is only true,
if both contrasts are not (solely) driven by the conjunctions. There is no
evidence in the paper that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).
